Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-06 SupportingInformation.Rmd
error fixed

  # for clayton with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

@@

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

@@

  # for survival clayton with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

@@

  # for gumbel with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

@@

  # for survival gumbel with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

>>>>

  # for clayton with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=p0,model=model)

@@

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=p0,model=model)

@@

  # for survival clayton with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=p0,model=model)

@@

  # for gumbel with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=p0,model=model)

@@

  # for survival gumbel with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=p0,model=model)
